MSCA 31006: Final Project - AQI Forecasting

### 2023-08-16 MSCA_31006_Time_Series_Final_Combined.Rmd
Update MSCA_31006_Time_Series_Final_Combined.Rmd

model_sarima_weekly <- auto.arima(train_weekly, 
                                  seasonal = TRUE, 
                                  stepwise = FALSE, #stepwise = TRUE,
                                  trace = FALSE,
                                  #m=52,
                                  #d=None,
                                  #D=1, # order of seasonal differencing
                                  lambda="auto",
                                  start.p = 1, max.p = 3,
                                  start.q = 2, max.q = 4)

>>>>

model_sarima_weekly <- auto.arima(train_weekly, 
                                  seasonal = TRUE, 
                                  lambda="auto",
                                  start.p = 1, 
                                  max.p = 3,
                                  start.q = 2, 
                                  max.q = 4)
